\mptext{cbrt}{6} Economic Status, Currency Exchange Rate (Turkish Lira - TRY), Inflation Rates, Interest Rates, Government Debt \& Fiscal Policy, and Foreign Trade Balance.

\begin{itemize}
    \item Economic Status: Represents the overall condition of the Turkish economy, including inflation, unemployment, and growth trends.
    \item Currency Exchange Rate (Turkish Lira - TRY): Fluctuations in the value of the Turkish lira relative to other currencies, influencing trade and inflation.
    \item Inflation Rates: Measures the rate of price increases for goods and services in Turkey, impacting purchasing power and policy decisions.
    \item Interest Rates: The CBRT's benchmark policy rate, affecting borrowing costs, investment, and overall economic activity.
    \item Government Debt \& Fiscal Policy: Represents Turkey’s government borrowing levels and fiscal management, influencing monetary policy choices.
    \item Foreign Trade Balance: Measures Turkey’s exports and imports, with trade surpluses or deficits impacting currency strength and policy decisions.
\end{itemize}

\paragraph{Examples:}
\begin{itemize}
    \item ``Thus, the unemployment rate declined by 0.4 points compared to previous month and realized as 9.6\%.''\\ 
    \textbf{Hawkish}: The sentence reports a decline in unemployment, potentially justifying a more hawkish approach to curb inflation.

    \item ``Thus, the rise in automobile prices amounted to 34.01\% in the first six months of 2023.''\\ 
    \textbf{Hawkish}: This sentence highlights a significant increase in automobile prices, suggesting potential inflationary pressures that may prompt a tighter monetary policy stance.
    
    \item ``The committee has therefore decided to keep the interest rates at current levels.''\\ 
    \textbf{Neutral}: The sentence simply states that interest rates will remain unchanged, reflecting no immediate bias toward tightening or easing policy.
    
    \item ``Annual inflation remained flat in rents, but decreased in other subgroups.''\\ 
    \textbf{Dovish}: With inflation showing stability in rents and declines elsewhere, the overall price pressure appears subdued, which may support expansionary monetary policy.
    
    \item ``In sum, economic activity is expected to recede in the third quarter.''\\ 
    \textbf{Dovish}: This forward-looking forecast of a slowdown in economic activity points to the possibility of an easing monetary stance to promote economic growth.
    
    \item ``Impact analyses of the CBRT's regulations are conducted for all components of the framework by assessing their impact on inflation, interest rates, exchange rates, reserves, expectations, securities, and financial stability with a holistic approach.''\\ 
    \textbf{Irrelevant}: The sentence focuses on a comprehensive evaluation process of regulatory impacts without providing any specific insight into monetary policy stance.
\end{itemize}



\newpage

\begin{longtable}{p{0.118\textwidth}p{0.183\textwidth}p{0.183\textwidth}p{0.183\textwidth}p{0.183\textwidth}}
\caption{\mptitle{Central Bank of Turkey}}
\label{tb:cbrt_mp_stance_guide} \\
\toprule
\textbf{Category} & \textbf{Dovish} & \textbf{Hawkish} & \textbf{Neutral} & \textbf{Irrelevant} \\
\midrule
\endfirsthead
%
\toprule
\textbf{Category} & \textbf{Dovish} & \textbf{Hawkish} & \textbf{Neutral} & \textbf{Irrelevant} \\
\midrule
\endhead
%
\textbf{Economic Status} & When inflation is decreasing, unemployment is rising, or economic growth is weak. & When inflation is increasing, unemployment is low, and economic growth is strong. & When economic indicators remain stable. & Sentence is not relevant to monetary policy. \\
\midrule
\textbf{Currency Exchange Rate (Turkish Lira - TRY)} & When the lira depreciates significantly, increasing import costs and inflationary pressure. & When the lira appreciates, reducing import costs and signaling potential monetary tightening. & When the exchange rate remains stable. & Sentence is not relevant to monetary policy. \\
\midrule
\textbf{Inflation Rate} & When inflation is slowing down, suggesting room for rate cuts. & When inflation is rising, requiring tighter monetary policy. & When inflation remains within the target range. & Sentence is not relevant to monetary policy. \\
\midrule
\textbf{Money Supply} & Low money supply, any increase in M2, demand for loans is higher. & High money supply, demand for goods increase, demand for loans decrease. & N/A. & Sentence is not relevant to monetary policy. \\
\midrule
\textbf{Government Debt} & When government debt increases significantly, prompting expectations of monetary stimulus to manage borrowing costs. & When debt decreases, indicating fiscal discipline and allowing tighter monetary policy. & When debt levels remain stable. & Sentence is not relevant to monetary policy. \\
\midrule
\textbf{Foreign Trade Balance} & When the trade deficit widens, indicating higher imports than exports, potentially justifying a weaker lira and looser monetary policy. & When the trade deficit narrows or a surplus is recorded, strengthening the lira and allowing for tighter policy. & When the trade balance remains relatively unchanged. & Sentence is not relevant to monetary policy. \\
\midrule
\textbf{Key Words and Phrases} & When the sentiment is growth oriented, e.g., "accommodative," "maximum employment," "price stability," "heightened consumption," "low inflation." & When sentiment is restrictive, indicating a focus on "price stability" and "sustained growth." & Use of neutral terms, e.g., "mixed," "moderate," "reaffirmed." & Sentence is not relevant to monetary policy. \\
\bottomrule
\end{longtable}
