\mptext{pboc}{seven} Inflation, Value of the Yuan, Interest Rates, Money Supply, GDP Growth Rate, and Trade Output.
\begin{itemize}
    \item \textit{Inflation: }A sentence about the inflation rate in the country
    \item \textit{Value of the Yuan: }A sentence about how the value of the Yuan is changing relative to the USD 
    \item \textit{Interest Rates: }A sentence about how interest rates, including the repo rate and loan prime rates are changing. 
    \item \textit{Money Supply: }A sentence pertaining the M2 money supply. PCB may conduct short-term liquidity operations and reverse repo operations to influence liquidity into the market.
    \item \textit{GDP Growth Rate: }A sentence pertaining to changes in GDP or changes in the commodities market or key industry that may impact the GDP
    \item \textit{Trade Output: }A sentence pertaining to China's export or import levels or how macroeconomic factors   may impact foreign trade 
\end{itemize}

\textbf{Examples:}
\begin{itemize}
    \item ``In line with the rules on monetary policy committee of the people's bank of china and with the approval of the state council, presidents of two wholly state-owned commercial banks, Liu Mingkang, Zhang Enzhao and Wu Jinglian will withdraw from the monetary policy committee as their term has expired.''
    \newline\textbf{Irrelevant:} Sentence is not directly related to monetary policy. 
    \item ``Improvement of the managed floating exchange rate regime should be effected, continuously following the principle of “making it a self-initiated, controllable and gradual process.''''
    \newline\textbf{Dovish: } The PBoC is confident in the health of the market is not concerned about the money supply becoming too large hence their sire to focus on floating the exchange rate.
    \item ``It was noted at the meeting that efforts should made to implement the prudent monetary policy, make the financial measures more targeted, flexible and effective, and give more priority to stabilizing the general price level in 2011.''
    \newline\textbf{Hawkish: }The PBoC feels that monetary policy needs to be implemented in order to stabilize prices, which is dovish. 
    \item ``The committee discussed monetary policy and measures to be adopted in the period ahead and concurred that the sound monetary policy should be preserved, interest rates of deposits and loans be maintained stable to ensure steady advancement of market-based interest rate reform.''
    \newline\textbf{Neutral: }The PBoC is emphasizing maintaining the currency policy.

\end{itemize}

\newpage

\begin{longtable}{p{0.118\textwidth}p{0.183\textwidth}p{0.183\textwidth}p{0.183\textwidth}p{0.183\textwidth}}
\caption{\mptitle{People's Bank of China}} \label{tb:pboc_mp_stance_guide}\\
\toprule
\textbf{Category} & \textbf{Hawkish} & \textbf{Dovish} & \textbf{Neutral} & \textbf{Irrelevant} \\
\midrule
\endfirsthead

\toprule
\textbf{Category} & \textbf{Hawkish} & \textbf{Dovish} & \textbf{Neutral} & \textbf{Irrelevant} \\
\midrule
\endhead
\textbf{Inflation} & When inflation rates rise inflationary pressures. & When inflation rates fall. & When inflation rate is stable. & Sentence is not relevant to monetary policy. \\
\midrule
\textbf{Value of the Yuan} & When Yuan depreciates. & When Yuan appreciates. & When Yuan remains stable. & Sentence is not relevant to monetary policy. \\
\midrule
\textbf{Interest Rates} & When the repo rate increases or loan prime rates (LPR) are increased. & When repo rate decreases or when short-term rates are lowered. & When interest rates are maintained at the same level. & Sentence is not relevant to monetary policy. \\
\midrule
\textbf{Money Supply} & When M2 money supply is decreasing. & When PBC restricts money supply. & When money supply remains the same. & Sentence is not relevant to monetary policy. \\
\midrule
\textbf{GDP Growth Rate} & When GDP growth declines. & When GDP growth increases or when measures will be taken to promote real economic growth. & When GDP growth remains constant. & Sentence is not relevant to monetary policy. \\
\midrule
\textbf{Trade Output} & When policy aims to decreasing foreign trade. & When there are bottlenecks key industries namely oil, coal, and electricity, or sluggish global economy, or other hindrances to foreign trade. & When there is a focus on maintaining stability in trade. & Sentence is not relevant to monetary policy. \\
\bottomrule
\end{longtable}
