\mptext{cbe}{12} exchange rate, inflation, real GDP, foreign investment, employment, foreign debt, interest rates, poverty, tourism, oil and natural gas, remittance payments, and Suez Canal. Each sentence is labeled as hawkish, dovish, neutral, or irrelevant.
\begin{itemize}
    \item \emph{Exchange rate}: Sentence pertaining to the value of Egyptian Pound (EGP) against United States Dollar (USD).
    \item \emph{Inflation}: A sentence pertaining past or current inflation levels, changes in inflation, or target inflation.
    \item \emph{Real GDP}: A sentence about changes to Egypt's economic output or target GDP.
    \item \emph{Employment}: A sentence about changes to the employment levels in Egypt or target employment levels.
    \item \emph{Foreign Investment}: A sentence about the level of foreign assets Egypt has or changes to foreign assets.
    \item \emph{Foreign Debt}: A sentence regarding the level of foreign debt in Egypt or changes to foreign debt.
    \item \emph{Interest Rates}: A sentence pertaining to past or current interest rate levels, changes to interest rate or target interest rate.
    \item \emph{Poverty}: A sentence pertaining to current poverty levels or changes to poverty levels.
    \item \emph{Tourism}: A sentence pertaining to current tourism revenue or foreseeable or past changes to tourism revenue.
    \item \emph{Oil and Natural Gas}: A sentence pertaining to changes in oil or natural gas prices, supply, demand, or exports, or a sentence regarding the affect on Egypt's economy due to global oil prices or global oil demand. Note oil and natural gas includes crude oil, petroleum, and petroleum derivatives.
    \item \emph{Remittance Payments}: A sentence pertaining to changes in level of remittance payments as a function of GDP.
    \item \emph{Suez Canal}: A sentence regarding the number of or change to the number of cargo ships passing through the Suez Canal, or geopolitical factors that may affect Suez Canal revenue.
\end{itemize}


\textbf{Examples}: 
\begin{itemize}
    \item ``With the gradual easing of previous shocks, inflationary pressures continued to subside, as annual headline and core inflation edged downward for the fifth consecutive month to reach 25.7 percent and 24.4 percent in July 2024, respectively.''\\
    \textbf{Dovish}: The inflation rate has consistently been decreasing suggesting that the MPC will decrease interest rates. 
    \item ``The slight increase in the remittances of the Egyptians working abroad by 1.6 percent to register US \$ 31.9 billion.''\\
    \textbf{Hawkish}: Increase in remittance payments means larger money supply in Egypt and more economic activity, increase the money supply in the market. Therefore, MPC would increase interest rates. 
    \item ``Globally, the expansion of economic activity continued to weaken, financial conditions eased, and trade tensions continued to weigh on the outlook.''\\
    \textbf{Neutral}: Both hawkish and dovish sentiment are expressed. Weakened economic growth and trade tensions indicates decreasing interest rates but easing financial conditions suggests that may not be necessary.
    \item ``The MPC is watching these developments and is weighing the possible effects of the above on inflation in the near future.''\\
    \textbf{Irrelevant}: There is missing information that makes the Stance unclear.
\end{itemize}

\newpage


\begin{longtable}{p{0.118\textwidth}p{0.183\textwidth}p{0.183\textwidth}p{0.183\textwidth}p{0.183\textwidth}}
\caption{\mptitle{Central Bank of Egypt}} \\
\toprule
\textbf{Category} & \textbf{Hawkish} & \textbf{Dovish} & \textbf{Neutral} & \textbf{Irrelevant} \\
\midrule
\endfirsthead

\toprule
\textbf{Category} & \textbf{Hawkish} & \textbf{Dovish} & \textbf{Neutral} & \textbf{Irrelevant} \\
\midrule
\endhead

\textbf{Exchange rate} & When exchange rate of EGP against USD increases. & When exchange rate of EGP against USD decreases. & When exchange rate remains stable. & Sentence is not relevant to monetary policy. \\
\midrule
\textbf{Inflation} & When inflation or CPI increases or when mention of  maintaining a flexible inflation target, "price stability over the medium term", mandate, structural reform, or some adjacent topic. & When inflation or CPI decreases. & When inflation remains unchanged or changes minimally. & Sentence is not relevant to monetary policy. \\
\midrule
\textbf{Real GDP} & When real GDP growth is strong. & When real GDP growth rate in Egypt is sluggish. & When GDP remains steady, stable, or unchanged. & Sentence is not relevant to monetary policy. \\
\midrule
\textbf{Employment} & When unemployment levels decrease. & When unemployment levels increase. & No or negligible changes to unemployment levels. & Sentence is not relevant to monetary policy. \\
\midrule
\textbf{Foreign Investment} & When there is an increase in foreign assets in Egypt. & When there is a decrease in foreign assets in Egypt. & When amount of foreign assets remain unchanged. & Sentence is not relevant to monetary policy. \\
\midrule
\textbf{Foreign Debt} & When Egypt reduces its foreign debt or secures debt relief, improving fiscal balance. & When Egypt's foreign debt increases, raising repayment pressure and fiscal instability. & When foreign debt levels remain manageable with regular servicing or foreign debt levels remain unchanged. & Sentence is not relevant to monetary policy. \\
\midrule
\textbf{Interest Rates} & When interest rates increase. & When interest rates decrease. & When interest rates remain unchanged. & Sentence is not relevant to monetary policy. \\
\midrule
\textbf{Poverty} & When poverty rate decreases indicating economic recovery or raising inflation. & While inflation might stabilize, economic growth slows, increasing poverty levels. & When poverty rate remains unchanged. & Sentence is not relevant to monetary policy. \\
\midrule
\textbf{Tourism} & When tourism revenue increases. & When tourism revenue declines. & When tourism revenue remains steady. & Sentence is not relevant to monetary policy. \\
\midrule
\textbf{Oil and Natural Gas} & When global oil/gas prices surge, leading to higher energy export revenues but potentially higher domestic energy costs. & When global oil/gas prices drop, lowering export revenues but reducing domestic fuel costs. & When oil/gas prices and exports remain stable, providing steady revenue without major shocks. & Sentence is not relevant to monetary policy. \\
\midrule
\textbf{Remittance payments} & When remittance payments decrease as a percentage of GDP. & When remittance payments increase as a percentage of GDP. & When remittance payments remain unchanged. & Sentence is not relevant to monetary policy. \\
\midrule
\textbf{Suez Canal} & When the number of cargo ships increases, boosting Suez Canal revenue. & When the number of cargo ships declines, affecting Suez Canal revenue, usually due to a war in the region or blockage in the Red Sea. & When the number of cargo ships passing through the canal doesn’t change. & Sentence is not relevant to monetary policy. \\
\bottomrule
\label{tb:cbe_mp_stance_guide}
\end{longtable}
