\mptext{bsp}{five} Policy, Environment, Society, Market, and Trade.

\begin{itemize}
    \item \emph{Policy}: Decisions implemented by the government or its institutions to regulate, direct, or influence national affairs. Policies often impact laws and public services.
    \item \emph{Environment}: Decisions related to environmental sustainability, energy consumption, or natural resources.
    \item \emph{Society}: Decisions aimed at addressing the well-being of society. Policies often address income inequality, cost-of-living, and social programs.
    \item \emph{Market}: Decisions that influence financial markets, including changes in interest rates, bond yields, and liquidity management.
    \item \emph{Trade}: Decisions that impact trade, including imports, exports, exchange rates, and trade balances.
\end{itemize}

\paragraph{Examples: }
\begin{itemize}
    \item ``Maintain the BSP’s policy interest rates at 7.5 percent for the overnight RRP (borrowing) rate and 9.75 percent for the overnight RP (lending) rate; b.''\\
    \textbf{Neutral}: Maintaining existing interest rates indicates no change in monetary policy.
    
    \item ``The Monetary Board (MB) decided to: a) Increase the BSP’s key policy interest rate by 50 basis points to 4.50 percent for the overnight RRP (borrowing) facility, effective 28 September 2018; and, b) Adjust the interest rates on the overnight deposit and overnight lending facilities accordingly.''\\
    \textbf{Hawkish}: Increase in interest rate and Reverse Repurchase Rate (RRP) signals contractionary monetary policy. 

    \item ``- In August, the peso depreciated against the US dollar amid renewed global recession concerns as a result of protracted trade conflict between the US and China.''\\
    \textbf{Hawkish}: A depreciating peso in addition to recession concerns is likely to drive inflation higher, creating a need for contractionary monetary policy to ensure the stability of the peso and the economy.
    
    \item ``Moreover, unemployment rose to 10.2 percent in the fourth quarter of 2002 as against 9.8 percent in the same period a year ago.''\\
    \textbf{Dovish}: A sharp increase in the unemployment rate signals monetary easing to stimulate the economy. 

    \item ``Compared to the previous policy meeting, baseline inflation forecast for 2013 has been revised downward due primarily to lower oil prices.''\\
    \textbf{Dovish}: Lower inflation forecasts indicate room for monetary easing without the risks of high inflation.

    \item ``The highlights of the discussions during the 9 November 2017 monetary policy meeting were approved by the Monetary Board during its regular meeting held on 28 November 2017.''\\
    \textbf{Irrelevant}: The sentence mentions the approval of a past discussion with no mention of a monetary policy stance.
\end{itemize}

\newpage

\begin{longtable}{p{0.118\textwidth}p{0.183\textwidth}p{0.183\textwidth}p{0.183\textwidth}p{0.183\textwidth}}
\caption{Annotation Guide} \label{tb:bsp_mp_stance_guide} \\
\toprule
\textbf{Category} & \textbf{Dovish} & \textbf{Hawkish} & \textbf{Neutral} & \textbf{Irrelevant} \\
\midrule
\endfirsthead

\toprule
\textbf{Category} & \textbf{Dovish} & \textbf{Hawkish} & \textbf{Neutral} & \textbf{Irrelevant} \\
\midrule
\endhead
\textbf{Policy} & When government spending decreases or financial regulations are tightened. & When government spending increases or financial regulations are loosened. & When policy statements maintain current spending levels or regulations. & Sentence is not relevant to monetary policy. \\
\midrule
\textbf{Environment} & Energy prices fall, new price controls are implemented on fossil fuels, added subsidies for renewable energy, adverse effects of el niño. & Energy prices rise, production costs rise, or subsidies are removed. & When statements maintain current prices, confirm existing policy (e.g. subsidies, price controls) without signaling change. & Sentence is not relevant to monetary policy. \\
\midrule
\textbf{Society} & When there is higher taxes, reduced subsidies, reduced social programs, or reduced minimum wages. & When there are lower taxes, increased subsidies, new social programs, or increases in minimum wages. & When societal measures are discussed with no clear indication of change to fields such as taxes, minimum wage, subsidies, or social programs. & Sentence is not relevant to monetary policy. \\
\midrule
\textbf{Market} & When there is a reduction in interest rates, increase in the money supply, higher demand for loans, narrowing bond spread, higher bond yields. & Where there is an increase in interest rates, decrease in money supply, lower demand for loans, expanding bond spread, lower bond yields. & When there is no change in interest rates, money supply, or demand for loans. & Sentence is not relevant to monetary policy. \\
\midrule
\textbf{Trade} & Philippine peso appreciates, increased trade deficit, decreased exports. & Philippine peso depreciates, increased trade surplus, increased imports. & Maintained trade activity and currency valuation. & Sentence is not relevant to monetary policy. \\
\midrule
\bottomrule
\end{longtable}
