\mptext{ecb}{nine} Economic Status, Euro Value Change, Energy Prices, House Prices, Foreign Nations, ECB Expectations/Actions/Assets, Money Supply, Key Words/Phrases, and Labor.

\begin{itemize} 
    \item \emph{Economic Status}: A sentence pertaining to the general state of the Eurozone economy, incorporating factors such as inflation trends, GDP performance, and overall growth risks. 
    \item \emph{Euro Value Change}: A sentence that addresses variations in the Euro's value relative to other global currencies, whether it appreciates or depreciates. 
    \item \emph{Energy Prices}: A sentence relating to changes in energy costs within the Eurozone, including fluctuations in oil and natural gas prices. 
    \item \emph{House Prices}: A sentence that discusses shifts in the residential real estate market within the Eurozone, particularly changes in housing prices. 
    \item \emph{Foreign Nations}: A sentence concerning trade relations between the European Union and non-Eurozone countries, highlighting changes in trade deficits or external demand for EU goods. 
    \item \emph{ECB Expectations, Actions, and Assets}: A sentence describing the European Central Bank's economic outlook and policy responses, including interest rate adjustments and modifications to asset purchasing programs. 
    \item \emph{Money Supply}: A sentence discussing the availability of monetary resources in the Eurozone, reflecting trends in bank capitalization, changes in the M2 measure, and shifts in loan demand. 
    \item \emph{Key Words and Phrases}: A sentence that includes specific terminology or expressions frequently used by policymakers to indicate a dovish, hawkish, or neutral stance. 
    \item \emph{Labor}: A sentence addressing labor market conditions, including fluctuations in unemployment rates and changes in salaries. 
\end{itemize}


\paragraph{Examples}
\begin{itemize}
    \item ``The purchasing managers’ index for manufacturing export orders had fallen into contractionary territory in march owing to the war in Ukraine and lockdowns in China.'' \newline
    \textbf{Dovish}: Slowing economic growth in the manufacturing sector is highlighted, signifying that the central bank may want to lower interest rates to stimulate the economy.
    
    \item ``In addition, options markets had, by and large, priced out low inflation outcomes over the following five years.'' \newline
    \textbf{Hawkish}: Future inflation expectations are high, suggesting that higher inflation may be to come, and the ECB may want to start contracting the money supply.
    
    \item ``Current interest rates are at levels that, maintained for a sufficiently long duration, will make a substantial contribution to this goal.'' \newline
    \textbf{Neutral}: The ECB reiterates that there will be no interest rate change.
    
    \item ``Labour costs had also confirmed continued moderate domestic price pressures.'' \newline
    \textbf{Hawkish}: High labor costs can lead to inflation, which may encourage the ECB to decrease the money supply.
    
    \item ``Data on new export orders pointed to a sharp fall of global trade in the second quarter of the year.'' \newline
    \textbf{Dovish}: This sentence indicates a significant decline in global trade, suggesting economic slowdown that may prompt policymakers to adopt a more dovish monetary policy stance.
    
    \item ``Against this background, it was recalled that the ECB also had secondary objectives.'' \newline
    \textbf{Irrelevant}: This sentence primarily references the ECB’s secondary objectives, which does not directly relate to immediate monetary policy actions.
\end{itemize}

\newpage

\begin{longtable}{p{0.118\textwidth}p{0.183\textwidth}p{0.183\textwidth}p{0.183\textwidth}p{0.183\textwidth}}
\caption{\mptitle{European Central Bank}} \\
\toprule
\textbf{Category} & \textbf{Hawkish} & \textbf{Dovish} & \textbf{Neutral} & \textbf{Irrelevant} \\
\midrule
\endfirsthead

\toprule
\textbf{Category} & \textbf{Hawkish} & \textbf{Dovish} & \textbf{Neutral} & \textbf{Irrelevant} \\
\midrule
\endhead
\textbf{Economic Status} & HICP Inflation increases or is higher than targeted 2\% rate, Inflation risk present on high side, Eurozone GDP and/or Eurozone GDP growth increases. & HICP Inflation decreases or is lower than targeted 2\% rate, Eurozone GDP and/or Eurozone GDP growth decreases, Economic growth risk present on the downside. & Inflation rate remains stable around 2\%, Economic growth remains unchanged. & Sentence is not relevant to monetary policy. \\
\midrule
\textbf{Euro Value Change} & Euro depreciates relative to other global currencies. & Euro appreciates relative to other global currencies. & Minimal or no change in the Euro Value relative to other global currencies. & Sentence is not relevant to monetary policy. \\
\midrule
\textbf{Energy Prices} & Energy prices in the Eurozone, including oil and or natural gas prices, increase. & Energy prices in the Eurozone, including oil and or natural gas prices, decrease. & N/A & Sentence is not relevant to monetary policy. \\
\midrule
\textbf{House Prices} & Housing prices in the Eurozone increase. & Housing price in the Eurozone decrease. & N/A & Sentence is not relevant to monetary policy. \\
\midrule
\textbf{Foreign Nations} & European Union trade deficit increases. & European Union trade deficit decreases, external (to Eurozone) demand for EU goods falls. & When foreign nation outside of the Eurozone or European Union is discussed. & Sentence is not relevant to monetary policy. \\
\midrule
\textbf{ECB Expectations, Actions, and Assets} & Inflation, Economic Growth higher than expected, Increase in key ECB interest rates, Selling off of Securities purchased through Purchasing Programs). & Inflation, Economic Growth lower than expected, Decrease in key ECB interest rates, Increase in or continued exercise of purchasing programs. & Inflation, Economic Growth near expectations, Unchanged ECB interest rates (Deposit Facility, Fixed Rate Tender, Marginal Lending), no change in purchasing program policy. & Sentence is not relevant to monetary policy. \\
\midrule
\textbf{Money Supply} & Money supply is high, High Capitalization of banks, M2 decreases, Low demand for loans. & Money supply is low, Low capitalization for banks, M2 increases, Increased demand for loans. Ex. "Banks reported, on balance, an increase in firms’ demand for loans or drawing of credit lines in the second quarter of 2022". & N/A & Sentence is not relevant to monetary policy. \\
\midrule
\textbf{Key Words and Phrases} & Indicating a focus on ``price stability'' and ``sustained growth.'' & When the stance is ``accommodative,'' a focus on ``maximum employment.'' & Use of phrases like ``mixed,'' ``moderate,'' ``reaffirmed.'' & Sentence is not relevant to monetary policy. \\
\midrule
\textbf{Labor} & When unemployment rate decreases or earnings increase. & When unemployment rate increases or earnings decrease. & Unemployment rate or growth is unchanged. & Sentence is not relevant to monetary policy. \\
\bottomrule
\label{tb:ecb_mp_stance_guide}
\end{longtable}